---
title: "Guss the Number"
author: "Ahmed Gad"
date: "October 24, 2015"
output: html_document
---

The function below will generate a random number on each run of the application:
-------

```{r , eval= F}
numberGuessed <- function(guess, number) {
    returnValue <- "Nothing entered yet."
    if (guess > 100) {
        #print(guess)
        #print(class(guess))
        #print(class(100))
        returnValue <- 'Above 100.\nPlease make a selection between 1 and 100.'
    }
    else if (guess < 1) {
        #print(guess)
        returnValue <- 'Below 1.\nPlease make a selection between 1 and 100.'
    }
    else if (guess > number) {
        returnValue <- 'Higher than the number.'
    }
    else if (guess < number) {
        returnValue <- 'Lower than the number.'
    }
    else if (guess == number) {
        returnValue <- 'Correct!'
    }
    returnValue
}
```


there will be an input text box for the user to enter his guss.
after that the function will return a message saying that is the entered number is Higher, lower, or just right to the generated number.

```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
